Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
memorability 2/6 distance

%TODO h - add another table, only abt memorability tho
%TODO  where is home? need to explain this part in system? make sure this is explained
\subsubsection{Distance}
% only affect location rememberance
% 0 - 100%, 1 - 75%, 2 - 72%, 3 - 44%, 4 - 52%, 5 - 10%, $\chi^2(5,179) = 18.106$, p < 0.01
The distance away from the participant’s home had differing effects on photo memorability and Rewind memorability (Figure~\ref{fig:distancememory}).

Photo memorability and distance had a clear linear relationship. As the distance increased, photo memorability decreased, suggesting that locations further away from home were less likely to be remembered. Remembrance was 100\% for Distance Group 0, or home. One participant recognized a photo because her ``husband's car is in the driveway.'' Remembrance dropped to 75\% for Distance Group 1, then down to 10\% for Distance Group 5, which represented the locations furthest away from home. These percentages are statistically significant, with a p-value of 0.0028.

There was no statistical significance for Rewind remembrance. Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except for distances that were close to home. While remembrance for almost all distance groups was on average near 60\%, remembrance for Rewinds in Distance Group 1 was 25\%. This data suggests that participants often did not remember or could not distinguish the exact trips occurring in locations close to their home, where most trips happen.

@@

\subsubsection{Other Variables}
% needs to be filled?

>>>>

%TODO h - add another table, only abt memorability tho
%TODO  where is home? need to explain this part in system? make sure this is explained
\subsubsection{Distance}
% only affect location rememberance
% 0 - 100%, 1 - 75%, 2 - 72%, 3 - 44%, 4 - 52%, 5 - 10%, $\chi^2(5,179) = 18.106$, p < 0.01
The depicted location's distance away from the participant’s home had differing effects on photo memorability and Rewind memorability. Photo memorability and distance had a clearly linear relationship, while the relationship between Rewind memorability and distance was more nuanced.

For photos, as the distance increased, memorability decreased, suggesting that locations further away from home were less likely to be remembered. In Distance Group 0, or the participant's home location, location recall was 100\%. One participant, upon recognition, explained that she knew the location because ``my husband's car is in the driveway.'' Further away in Distance Group 1, remembrance dropped to 75\%, then later down to 10\% for Distance Group 5, which represented the locations furthest away from home. These percentages are statistically significant, with a p-value of 0.0028.

%TODO find citation that humans travel most within x km of their home/work nodes
%TODO memory competition--similar memories compete for significance
For Rewind memorability, there was no statistical significance. Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except for distances that were close to home in Distance Group 1. While remembrance for all distance groups was between 50-60\%, remembrance for Rewinds in Distance Group 1 was 25\%. This data suggests that participants often did not remember or could not distinguish the exact trips that occurred in locations close to their home. This is where most trips happen, and therefore competition between similar memories would make it harder for a person to distinguish the specific trip they were on that generated the Rewind.

@@
